---
title: "Markdown File"
author: "Anonymous"
output: 
  html_document:
    toc: yes
    toc_depth: 6
    toc_float: true
    code_folding: show
fig_height: 5
editor_options: 
  markdown: 
    wrap: 72
---

the following exercises are a test in disguise what do you think about
the coding? can you think of any improvements to the following?

```{r Chunk 1: setup}
rm(list=ls()) #always clean up your environment!

library(tidyverse)
library(ggplot2)
```

# PROBLEM 1

Visualizing your data is important! Summary statistics can be highly
misleading, and simply plotting the data can reveal a lot more! Lets
look at the Anscombe's Quartet data. There are four different data sets.
Anscombe, F. J. (1973). "Graphs in Statistical Analysis". American
Statistician. 27 (1): 17--a21. <doi:10.1080/00031305.1973.10478966>.
JSTOR 2682899.

```{r Chunk 2: Load in data}
anscombe_quartet = readRDS("data/anscombe_quartet.rds")

#let's explore the dataset 

str(anscombe_quartet)
```

## what does the function str() do?

shows variables, how many + type

## let's check some summary statistics:

```{r Chunk 3: min max}
anscombe_quartet %>% group_by(dataset) %>% summarise(mean_x = mean(x), mean_y = mean(y), min_x = min(x), min_y = min(y), max_x = max(x), max_y = max(y), crrltn = cor(x, y))

```

## what do the summary statistics tell us about the different datasets?

same means but different min and max

## let's plot the data with ggplot:

```{r Chunk 4: plot}

ggplot(anscombe_quartet, aes(x = x, y = y)) + geom_point() + geom_smooth(method = "lm", formula = y ~ x) + facet_wrap(~dataset)

# save the plot
ggsave("anscombe_quartet.png", width = 20, height = 20, units = "cm")
```

## what do the plots tell us about the different datasets?

they have similar lines but different points

## describe the relationship between x and y in the different datasets.

positive relationship

## would linear regression be an appropriate statistical model to analyse the x-y relationship in each dataset?

not for dataset 4 as all x points are at 8 other than one is at 19

## what conclusions can you draw for the plots and summary statistics?

# PROBLEM 2

## load in the datasaurus dataset

```{r Chunk 5: dino}
datasaurus_dozen = readRDS("data/datasaurus_dozen.rds")

# explore the dataset
str(datasaurus_dozen)
```

## how many rows and columns does the datasaurus_dozen file have?

1846 x 3

## calculate the correlations and summary statistics for x and y in all datasets:

```{r Chunk 6: min max}
datasaurus_dozen %>%
  group_by(dataset) %>%
             summarise( mean_x = mean(x), mean_y = mean(y), min_x = min(x), min_y = min(y), max_x = max(x), max_y = max(y), crrltn = cor(x, y) )
```

## Plot the relationships between x and y in each dataset including the line of best fit.

```{r Chunk 7: graph}
ggplot(datasaurus_dozen, aes(x=x,y=y)) + geom_point() + geom_smooth(method = "lm",formula = y ~ x) + facet_wrap(~dataset)

#save the plot

ggsave("datasaurus_dozen.png", width = 20, height = 20, units = "cm")
```

## what conclusions can you draw for the plots and summary statistics?

they all have the same mean x and mean y but look very different
